I-CAH Adiposity Rebound Analysis

This file should be within your main directory of analysis. Within that directory should be a "ar_functions_folder" to store functions, and "ar_data_files_to_load" where files are saved and loaded. 

```{r, load software packages}
rm(list = ls())

#we first establish the location of the working directory where we keep everything, depending on whether it exists (i.e. which computer we are using)
#check C drive
#take the working directory otherwise, which should work every time
if(!exists("location_of_main_folder")){
  location_of_main_folder <- getwd()
}

#paste the name of our functions folder into the path name
location_of_functions_folder <-
  paste0(location_of_main_folder, "/ar_functions_folder/")

#load the function that loads all the libraries and sources
source(paste0(location_of_functions_folder, "load_ar_libraries_and_sources_function.R"))

#paste together the location of the data files - we don't load in the first file, but we need this location for the end
location_of_data_files <-
  paste0(location_of_main_folder, "/ar_data_files_to_load/")

#run the function, pointing it towards the functions folder
load_ar_libraries_and_sources_function(
  location_of_functions_folder=location_of_functions_folder,
  location_of_data_files=location_of_data_files
)
```

```{r, read in files and write column names for reference}
ar_participants <- ar_participants_original <- 
  read.csv("./2024-01-26_Data_extraction_adiposity_rebound/STUDY DATASET 202305_NL CAH adiposity (CAH) cah module_corrected.csv", header=T, na.strings="")

write.csv(ar_participants_original, "ar_participants_original.csv")
```

```{r, create column names and missing data percentage files to refer to}
column_names_and_missing_percentages_ar_participants <-
  data.frame(
    Column=colnames(ar_participants),
    Percentage_complete=NA
  )

#create a loop to report the percentage complete
for (i in 1:length(column_names_and_missing_percentages_ar_participants$Column)){
  each_column <- column_names_and_missing_percentages_ar_participants[i,1]

  column_names_and_missing_percentages_ar_participants[i,"Percentage_complete"] <- 
    round(100*
      sum(!is.na(ar_participants[,c(each_column)])) / 
      length(ar_participants[,c(each_column)]), digits=1)
}

dir.create("Column_Names_and_missing_percentages")
write.csv(column_names_and_missing_percentages_ar_participants, 
          "./Column_Names_and_missing_percentages/colnames_and_missing_percentage_ar_participants.csv", 
          row.names=F)
```

########################################
Type of CAH
########################################

the non classic CAH response can go into another column that we call 'type_of_cah'. This can be created from 'Specify.the.actual.diagnosis...Details.of.Condition' which contains some information about salt wasters, but realistically is very poorly completed

```{r, creation of type_of_cah column}
ar_participants$type_of_cah <- 
  ar_participants$Specify.the.actual.diagnosis...Details.of.Condition

#now we just correct for different spellings with grepl
ar_participants$type_of_cah <-
  ifelse(grepl(x=ar_participants$type_of_cah,
               pattern="Satwasting" , ignore.case = TRUE),
         "Salt_wasting",
         ar_participants$type_of_cah)
ar_participants$type_of_cah <-
  ifelse(grepl(x=ar_participants$type_of_cah,
               pattern="salt" , ignore.case = TRUE),
         "Salt_wasting",
         ar_participants$type_of_cah)
ar_participants$type_of_cah <-
  ifelse(grepl(x=ar_participants$type_of_cah,
               pattern="virilising" , ignore.case = TRUE),
         "Simple_virilising",
         ar_participants$type_of_cah)
ar_participants$type_of_cah <-
  ifelse(grepl(x=ar_participants$type_of_cah,
               pattern="late" , ignore.case = TRUE),
         "Non_classic",
         ar_participants$type_of_cah)
ar_participants$type_of_cah <-
  ifelse(grepl(x=ar_participants$type_of_cah,
               pattern="non-classic" , ignore.case = TRUE),
         "Non_classic",
         ar_participants$type_of_cah)


```

********************************************
creation of decimal age column for adiposity rebound data
********************************************

```{r, calculate a preliminary decimal age}
ar_participants$file_1_dob_posix <-
  as.POSIXct(ar_participants$Date.of.birth...Birth, format = "%d/%m/%Y")
ar_participants$file_1_visit_date_posix <-
  as.POSIXct(ar_participants$Date...CAH.Longitudinal.Data, format = "%d/%m/%Y")

ar_participants$Decimal.age.at.visit..calculated.by.formula..YEARFRAC.DOB.DOV.. <- 
  as.numeric(difftime(
    ar_participants$file_1_visit_date_posix,
    ar_participants$file_1_dob_posix,
    units = "days"
  )) / 362.5
```


Centres may be approached to manually correct outlying entries flagged as biologically or chronologically implausible

Original columns are retained 

```{r, creation of manually corrected columns for date, dob, height and weight and retention of original columns}
ar_participants$manually_corrected_longitudinal_date <- 
  ar_participants$Date...CAH.Longitudinal.Data

ar_participants$manually_corrected_dob <- 
  ar_participants$Date.of.birth...Birth

ar_participants$manually_corrected_height <- 
  as.numeric(ar_participants$Height..cm....CAH.Longitudinal.Data)

print("if the following number is negative you need to look down the height_numeric_conversion_check")

length(unique(ar_participants$Height..cm....CAH.Longitudinal.Data)) -
  length(unique(ar_participants$manually_corrected_height))

height_numeric_conversion_check <-
  subset(ar_participants[,c(
    "Register.ID...Record",
    "Height..cm....CAH.Longitudinal.Data",
    "manually_corrected_height")],
         !is.na(Height..cm....CAH.Longitudinal.Data) & 
           is.na(manually_corrected_height) |
         is.na(Height..cm....CAH.Longitudinal.Data) & 
           !is.na(manually_corrected_height) )

height_mistake <-
  subset(
    ar_participants, Register.ID...Record %in% height_numeric_conversion_check$Register.ID...Record
  )

ar_participants$manually_corrected_weight <- 
  as.numeric(ar_participants$Weight..kg....CAH.Longitudinal.Data)

print("if the following number is negative you need to look down the weight_numeric_conversion_check")

length(unique(ar_participants$Weight..kg....CAH.Longitudinal.Data)) -
  length(unique(ar_participants$manually_corrected_weight))

weight_numeric_conversion_check <-
  subset(ar_participants[,c(
    "Register.ID...Record",
    "Weight..kg....CAH.Longitudinal.Data",
    "manually_corrected_weight")],
         !is.na(Weight..kg....CAH.Longitudinal.Data) & 
           is.na(manually_corrected_weight) |
         is.na(Weight..kg....CAH.Longitudinal.Data) & 
           !is.na(manually_corrected_weight) )

weight_mistake <-
  subset(
    ar_participants, Register.ID...Record %in% weight_numeric_conversion_check$Register.ID...Record
  )

ar_participants$Date...CAH.Longitudinal.Data_original <- 
  ar_participants$Date...CAH.Longitudinal.Data

ar_participants$Date.of.birth...Birth_original <- 
  ar_participants$Date.of.birth...Birth

ar_participants$Height..cm....CAH.Longitudinal.Data_original <- 
  ar_participants$Height..cm....CAH.Longitudinal.Data

ar_participants$Weight..kg....CAH.Longitudinal.Data_original <- 
  ar_participants$Weight..kg....CAH.Longitudinal.Data

ar_participants$BMI...CAH.Longitudinal.Data_original <- 
  ar_participants$BMI...CAH.Longitudinal.Data
```

```{r, assessment of BMI in context of no data entry for height or weight}
#in order to learn anything from the data field BMI, we would need BMI without weight or BMI without height
ar_participants$bmi_without_weight <-
  ifelse(!is.na(ar_participants$BMI...CAH.Longitudinal.Data) &
           is.na(ar_participants$Weight..kg....CAH.Longitudinal.Data),
         1,
         0)
print("number of bmi without weight:")
sum(ar_participants$bmi_without_weight)

ar_participants$bmi_without_height <-
  ifelse(!is.na(ar_participants$BMI...CAH.Longitudinal.Data) &
           is.na(ar_participants$Height..cm....CAH.Longitudinal.Data),
         1,
         0)
print("number of bmi without height:")
sum(ar_participants$bmi_without_height)

ar_participants_learn_from_bmi <-
  subset(ar_participants, 
         bmi_without_weight==1 | 
         bmi_without_height==1)

ar_participants_learn_from_bmi <-
  subset(ar_participants_learn_from_bmi, 
         Register.ID...Record %in% ar_participants_learn_from_bmi$Register.ID...Record)

ar_participants_learn_from_bmi <- 
  ar_participants_learn_from_bmi[,c(
  "Register.ID...Record",
  "Decimal.age.at.visit..calculated.by.formula..YEARFRAC.DOB.DOV..",
  "manually_corrected_height",
  "Height..cm....CAH.Longitudinal.Data_original",
  "manually_corrected_weight",
  "Weight..kg....CAH.Longitudinal.Data_original",
  "BMI...CAH.Longitudinal.Data",
  "bmi_without_height",
  "bmi_without_weight"
)]
```

```{r, back calculate height or weight from BMI if the former is missing}
#if we have BMI and weight but we don't have height, then back calculate height
ar_participants$manually_corrected_height <-
  ifelse(!is.na(ar_participants$BMI...CAH.Longitudinal.Data) &
          !is.na(ar_participants$Weight..kg....CAH.Longitudinal.Data) &
          is.na(ar_participants$Height..cm....CAH.Longitudinal.Data),
         100*(ar_participants$Weight..kg....CAH.Longitudinal.Data /
          ar_participants$BMI...CAH.Longitudinal.Data)^0.5,
  ar_participants$manually_corrected_height)

#if we have BMI and height but we don't have weight, then back calculate weight
ar_participants$manually_corrected_weight <-
  ifelse(!is.na(ar_participants$BMI...CAH.Longitudinal.Data) &
          !is.na(ar_participants$Height..cm....CAH.Longitudinal.Data) &
          is.na(ar_participants$Weight..kg....CAH.Longitudinal.Data),
         ar_participants$BMI...CAH.Longitudinal.Data *
          ((as.numeric(ar_participants$Height..cm....CAH.Longitudinal.Data)/100)^2),
  ar_participants$manually_corrected_weight)

#tell me how many we back calculated height for
ar_participants$back_calculated_height <-
  ifelse(!is.na(ar_participants$BMI...CAH.Longitudinal.Data) &
          !is.na(ar_participants$Weight..kg....CAH.Longitudinal.Data) &
          is.na(ar_participants$Height..cm....CAH.Longitudinal.Data),
         1,
  0)

sum(ar_participants$back_calculated_height)

#tell me how many we back calculated weight for
ar_participants$back_calculated_weight <-
  ifelse(!is.na(ar_participants$BMI...CAH.Longitudinal.Data) &
          !is.na(ar_participants$Height..cm....CAH.Longitudinal.Data) &
          is.na(ar_participants$Weight..kg....CAH.Longitudinal.Data),
         1,
  0)

sum(ar_participants$back_calculated_weight)

view_back_calculated_weight <- 
  subset(ar_participants, back_calculated_weight==1)[,c(
  "Register.ID...Record",
  "Decimal.age.at.visit..calculated.by.formula..YEARFRAC.DOB.DOV..",
  "manually_corrected_height",
  "Height..cm....CAH.Longitudinal.Data_original",
  "manually_corrected_weight",
  "Weight..kg....CAH.Longitudinal.Data_original",
  "BMI...CAH.Longitudinal.Data"
)]

view_back_calculated_height <- 
  subset(ar_participants, back_calculated_height==1)[,c(
  "Register.ID...Record",
  "Decimal.age.at.visit..calculated.by.formula..YEARFRAC.DOB.DOV..",
  "manually_corrected_height",
  "Height..cm....CAH.Longitudinal.Data_original",
  "manually_corrected_weight",
  "Weight..kg....CAH.Longitudinal.Data_original",
  "BMI...CAH.Longitudinal.Data"
)]
```


```{r, check back calculated weights}
ggplot(data=subset(ar_participants, back_calculated_weight==1)) +
  geom_point(aes(x=Decimal.age.at.visit..calculated.by.formula..YEARFRAC.DOB.DOV..,
                 y=manually_corrected_weight)) +
               labs(title="check these back calculated weights make sense for age:")
```


```{r, check back calculated heights}
ggplot(data=subset(ar_participants, back_calculated_height==1)) +
  geom_point(aes(x=Decimal.age.at.visit..calculated.by.formula..YEARFRAC.DOB.DOV..,
                 y=manually_corrected_height)) +
               labs(title="check these back calculated heights make sense for age:")
```



###################################
assessment of hypertension and antihypertensives columns
###################################

to flag people on antihypertensives, these columns were reviewed manually to ensure consistency and anyone who has any hint of treatment or diagnosis to be flagged

```{r, creation of manuallycorrected columns related to hypertension}
ar_participants$manually_corrected_hypertension_diagnosis_yes_no <-
  ar_participants$Hypertension...Comorbid.Conditions.and.Surgery

ar_participants$manually_corrected_hypertension_note <-
  ar_participants$Hypertension.note...Comorbid.Conditions.and.Surgery

ar_participants$manually_corrected_antihypertensives_yes_no <-
  ar_participants$Antihypertensives...Current.Medication

ar_participants$manually_corrected_antihypertensives_note <-
  ar_participants$Antihypertensives.note...Current.Medication
```


####################################
Manual data correction report for this file
####################################

```{r, %% number of values changed for Specify.the.actual.diagnosis...Details.of.Condition to type_of_cah }
ar_participants$type_of_cah_changed <-
  ifelse(ar_participants$Specify.the.actual.diagnosis...Details.of.Condition != 
           ar_participants$type_of_cah,
         1,
         0)
sum(ar_participants$type_of_cah_changed, na.rm=T)
sum((ar_participants$type_of_cah_changed==0), na.rm=T)
```

```{r, %% number of values changed for manually_corrected_longitudinal_date}
ar_participants$manually_corrected_longitudinal_date_changed <-
  ifelse(ar_participants$manually_corrected_longitudinal_date !=
           ar_participants$Date...CAH.Longitudinal.Data |
         is.na(ar_participants$manually_corrected_longitudinal_date) &
           !is.na(ar_participants$Date...CAH.Longitudinal.Data) |
         !is.na(ar_participants$manually_corrected_longitudinal_date) &
           is.na(ar_participants$Date...CAH.Longitudinal.Data)
           ,
         1,
         0)

print("Number manually_corrected_longitudinal_date_changed")
sum(ar_participants$manually_corrected_longitudinal_date_changed, na.rm=T)

print("Number manually_corrected_longitudinal_date_ NOT changed")
sum((ar_participants$manually_corrected_longitudinal_date_changed==0), na.rm=T)

print("Number without longitudinal date")
sum(is.na(ar_participants$Date...CAH.Longitudinal.Data))

sum(!is.na(ar_participants$Date...CAH.Longitudinal.Data))

sum(ar_participants$manually_corrected_longitudinal_date_changed, na.rm=T) + 
  sum((ar_participants$manually_corrected_longitudinal_date_changed==0), na.rm=T) -
  nrow(ar_participants)

nrow(ar_participants)

```

```{r, %% Create ar_participants_with_longitudinal_date}
print("Create ar_participants_with_longitudinal_date for assessment of other columns")

ar_participants_with_longitudinal_date <- 
  subset(ar_participants, !is.na(Date...CAH.Longitudinal.Data))

nrow(ar_participants_with_longitudinal_date)
```

```{r, %% number of values changed for manually_corrected_dob}
ar_participants_with_longitudinal_date$manually_corrected_dob_changed <-
  ifelse(  
    ar_participants_with_longitudinal_date$manually_corrected_dob !=
    ar_participants_with_longitudinal_date$Date.of.birth...Birth ,
         1,
         0)

ar_participants_with_longitudinal_date_single_id <-
  unique(ar_participants_with_longitudinal_date[,c("Register.ID...Record",
                     "manually_corrected_dob_changed")])

print("Number of patients with dob manually corrected")
sum(ar_participants_with_longitudinal_date_single_id$manually_corrected_dob_changed, na.rm=T)

print("Number of patients with dob not manually corrected")
sum((ar_participants_with_longitudinal_date_single_id$manually_corrected_dob_changed==0), na.rm=T)

print("Total number of patients in the extraction:")
nrow(ar_participants_with_longitudinal_date_single_id)

print("Number of patients not counted - this should be zero")
sum(ar_participants_with_longitudinal_date_single_id$manually_corrected_dob_changed, na.rm=T) + 
  sum((ar_participants_with_longitudinal_date_single_id$manually_corrected_dob_changed==0), na.rm=T) -
  nrow(ar_participants_with_longitudinal_date_single_id)
```

```{r, %% number of values changed for height}
ar_participants_with_longitudinal_date$manually_corrected_height_changed <-
  ifelse(ar_participants_with_longitudinal_date$manually_corrected_height !=
  ar_participants_with_longitudinal_date$Height..cm....CAH.Longitudinal.Data |
         is.na(ar_participants_with_longitudinal_date$manually_corrected_height) &
           !is.na(ar_participants_with_longitudinal_date$Height..cm....CAH.Longitudinal.Data) |
         !is.na(ar_participants_with_longitudinal_date$manually_corrected_height) &
           is.na(ar_participants_with_longitudinal_date$Height..cm....CAH.Longitudinal.Data),
         1,
         0)

print("Number of visits with manually corrected height")
sum(ar_participants_with_longitudinal_date$manually_corrected_height_changed, na.rm=T)

print("Number of visits with missing height")
sum(is.na(ar_participants_with_longitudinal_date$Height..cm....CAH.Longitudinal.Data), na.rm=T)

print("Number of visits with height")
sum(!is.na(ar_participants_with_longitudinal_date$manually_corrected_height_changed), na.rm=T)

print("Total number of visits with longitudinal date")
nrow(ar_participants_with_longitudinal_date)
```

```{r, %% number of values changed for weight}
ar_participants_with_longitudinal_date$manually_corrected_weight_changed <-
  ifelse(ar_participants_with_longitudinal_date$manually_corrected_weight !=
  ar_participants_with_longitudinal_date$Weight..kg....CAH.Longitudinal.Data |
         is.na(ar_participants_with_longitudinal_date$manually_corrected_weight) &
           !is.na(ar_participants_with_longitudinal_date$Weight..kg....CAH.Longitudinal.Data) |
         !is.na(ar_participants_with_longitudinal_date$manually_corrected_weight) &
           is.na(ar_participants_with_longitudinal_date$Weight..kg....CAH.Longitudinal.Data),
         1,
         0)

print("Number of visits with manually corrected weight")
sum(ar_participants_with_longitudinal_date$manually_corrected_weight_changed, na.rm=T)

print("Number of visits with missing weight")
sum(is.na(ar_participants_with_longitudinal_date$Weight..kg....CAH.Longitudinal.Data), na.rm=T)

print("Number of visits with weight")
sum(!is.na(ar_participants_with_longitudinal_date$manually_corrected_weight_changed), na.rm=T)

print("Total number of visits with longitudinal date")
nrow(ar_participants_with_longitudinal_date)
```

```{r, end of file so save all the listed dataframes into the parent directory}
save_ar_files_function(
  parent_directory = location_of_data_files,
  parent_file_name = "file_1")

Sys.time()
```
