
Load packages and reread files using the prebuilt load files function

```{r, load packages}
rm(list = ls())


#take the working directory otherwise, which should work every time
if(!exists("location_of_main_folder")){
  location_of_main_folder <- getwd()
}

#paste the name of our functions folder into the path name
location_of_functions_folder <-
  paste0(location_of_main_folder, "/ar_functions_folder/")

#load the function that loads all the libraries and sources
source(paste0(location_of_functions_folder, "load_ar_libraries_and_sources_function.R"))

#paste together the location of the data files - we don't load in the first file, but we need this location for the end
location_of_data_files <-
  paste0(location_of_main_folder, "/ar_data_files_to_load/")

#run the function, pointing it towards the functions folder
load_ar_libraries_and_sources_function(
  location_of_functions_folder=location_of_functions_folder,
  location_of_data_files=location_of_data_files
)

load_ar_files_function(previous_file_name = "file_3",
  parent_directory = location_of_data_files,
  list_of_data_frames_to_load=list("ar_participants_longitudinal_data",
                                   "ar_participants_base_data"))

load_ar_files_function(previous_file_name = "file_7", #note we now have unit imputation for unknown units of markers
  parent_directory = location_of_data_files,
  list_of_data_frames_to_load=list("ar_labs_wide"))

load_ar_files_function(previous_file_name = "file_8", #remember our conversion factors get saved once after being defined near to the meds frame and reloaded here 
  parent_directory = location_of_data_files,
  list_of_data_frames_to_load=list("ar_meds_wide",
                                   "prednisolone_to_hydrocortisone_conversion",
                                   "dexamethasone_to_hydrocortisone_conversion",
                                   "cortisone_acetate_to_hydrocortisone_conversion",
                                   "methylprednisolone_to_hydrocortisone_conversion"))

load_ar_files_function(previous_file_name = "file_9",
  parent_directory = location_of_data_files,
  list_of_data_frames_to_load=list("ar_fludro_wide"))
```


```{r, make all the id_visit_dates into characters before joining}
ar_meds_wide$id_visit_date <- 
  as.character(ar_meds_wide$id_visit_date)

ar_fludro_wide$id_visit_date <- 
  as.character(ar_fludro_wide$id_visit_date)

ar_participants_longitudinal_data$id_visit_date <- 
  as.character(ar_participants_longitudinal_data$id_visit_date)
ar_labs_wide$id_visit_date <- 
  as.character(ar_labs_wide$id_visit_date)

```

```{r, join ar_participants_longitudinal_data with ar_labs_wide}
#full join in ar_labs_wide to longitudinal data
a <- full_join(ar_participants_longitudinal_data, 
               ar_labs_wide, 
               by="id_visit_date")

check_frame_a <- 
  as.data.frame(freq(a$id_visit_date))

print("number without an id in the joined frame, which is the number with a ar_labs_wide visit but not a ar_participants_longitudinal_visit")
sum(is.na(a$id))

#create id again to find out what rows werent in the longitudinal data
a$id <- 
  gsub(x=a$id_visit_date, 
       pattern="_.*", 
       replacement="")

print("check everyone now has an ID - this number should be zero:")

sum(is.na(a$id))

```

```{r, join ar_participants_longitudinal_data and ar_labs_wide with ar_meds_wide}
#full join in ar_meds_wide
b <- full_join(a, 
               ar_meds_wide, 
               by="id_visit_date")

check_frame_b <- 
  as.data.frame(freq(b$id_visit_date))

print("number without an id in the joined frame, which is the number with a ar_meds_wide visit but not a ar_participants_longitudinal_visit or labs_wide visit")
sum(is.na(b$id))

b$id <- 
  gsub(x=b$id_visit_date, pattern="_.*", replacement="")
print("check everyone now has an ID - this number should be zero:")
sum(is.na(b$id))

```

```{r, join ar_participants_longitudinal_data and ar_labs_wide and ar_meds_wide with ar_fludro_wide}
#full join in fludro_wide
c <- full_join(b, 
               ar_fludro_wide, 
               by="id_visit_date")
print("number without an id in the joined frame, which is the number with a fludro_wide visit but not a ar_participants_longitudinal_visit, ar_meds_wide or ar_labs_wide visit")
sum(is.na(c$id))

e <- subset(b , grepl(x=id_visit_date, pattern="2933"))
e$id_visit_date
f <- subset(ar_fludro_wide , grepl(x=id_visit_date, pattern="2933"))
f$id_visit_date
print("this is the joined frame:")
d <- subset(c , grepl(x=id_visit_date, pattern="2933"))
d$id_visit_date

c$id <- 
  as.integer(gsub(x=c$id_visit_date, pattern="_.*", replacement=""))
print("check everyone now has an ID - this number should be zero:")

sum(is.na(c$id))

check_frame_c <- 
  as.data.frame(freq(c$id_visit_date))

print("number without an id in the joined frame, which is the number with a ar_fludro_wide visit but not a ar_participants_longitudinal_visit, ar_meds_wide or ar_labs_wide visit")
sum(is.na(c$id))
```

```{r, join ar_participants_longitudinal_data and ar_labs_wide and ar_meds_wide and ar_fludro_wide with ar_base_data}
ar_data <- 
  left_join(c, 
            ar_participants_base_data, 
            by="id")
check_frame_ar_data <- 
  as.data.frame(freq(c$id_visit_date))

ar_data$id <- 
  as.integer(gsub(x=ar_data$id_visit_date, pattern="_.*", replacement=""))

ar_data$visit_date <- 
  as.POSIXct(gsub(x=ar_data$id_visit_date, pattern=".*_", replacement=""), format="%Y-%m-%d")

print("Maximum number of rows per id_visit_date minus 1 (should be 0):")
as.numeric(max(
  subset(
    rownames_to_column(
      as.data.frame(
        freq(
          ar_data$id_visit_date))), 
    rowname !="Total" & rowname !="<NA>")$Freq)) - 1

ar_data <- 
  ar_data[order(ar_data$id,
                ar_data$visit_date),] 
```

```{r, correction for those not contained in the longitudinal or base data}
ar_data_visits_removed_for_no_base_data <-
  subset(ar_data, is.na(visit_in_base_data))

ar_data_patients_removed_for_no_base_data <-
  unique(ar_data_visits_removed_for_no_base_data$id)

number_of_rows_before_removal <- nrow(ar_data)
ar_data <-
  subset(ar_data, !is.na(visit_in_base_data))
number_of_rows_before_removal - nrow(ar_data)
```

```{r, recreate id and visit_date from id_visit_date, as well as creating visit_date_unix}
ar_data$id <- 
  as.integer(gsub(x=ar_data$id_visit_date, 
       pattern="_.*", 
       replacement=""))

ar_data$visit_date <- 
  as.POSIXct(gsub(x=ar_data$id_visit_date, 
       pattern=".*_", 
       replacement=""), 
       format="%Y-%m-%d")

ar_data$visit_date_unix <- 
  as.numeric(ar_data$visit_date)

print("number of missing id")
sum(is.na(ar_data$id))

print("number of missing id_visit_date")
sum(is.na(ar_data$id_visit_date))

print("number of missing visit_date")
sum(is.na(ar_data$id_visit_date))

print("Total number of visits in data set:")
nrow(ar_data)


```

```{r, create original columns to compare to a t the end of adjustments}
ar_data$Glucocorticoids...Current.Medication_original <- ar_data$Glucocorticoids...Current.Medication
ar_data$Glucocorticoids.note...Current.Medication_original <- ar_data$Glucocorticoids.note...Current.Medication
ar_data$Fludrocortisone...Current.Medication_original <- ar_data$Fludrocortisone...Current.Medication
ar_data$Fludrocortisone.frequency...Current.Medication_original <- ar_data$Fludrocortisone.frequency...Current.Medication
ar_data$medicine_1_original <- ar_data$medicine_1
ar_data$GC_dose_1_original <- ar_data$GC_dose_1 
ar_data$meds_unit_1_original <- ar_data$meds_unit_1
ar_data$meds_time_1_original <- ar_data$meds_time_1
ar_data$meds_clock_time_1_original <- ar_data$meds_clock_time_1
ar_data$medicine_2_original <- ar_data$medicine_2
ar_data$GC_dose_2_original <- ar_data$GC_dose_2
ar_data$meds_unit_2_original <- ar_data$meds_unit_2
ar_data$meds_time_2_original <- ar_data$meds_time_2
ar_data$meds_clock_time_2_original <- ar_data$meds_clock_time_2
ar_data$medicine_3_original <- ar_data$medicine_3
ar_data$GC_dose_3_original <- ar_data$GC_dose_3
ar_data$meds_unit_3_original <- ar_data$meds_unit_3
ar_data$meds_time_3_original <- ar_data$meds_time_3
ar_data$meds_clock_time_3_original <- ar_data$meds_clock_time_3
ar_data$different_GC_used_on_same_day_original <- ar_data$different_GC_used_on_same_day
ar_data$absolute_daily_GC_dose_sum_original <- ar_data$absolute_daily_GC_dose_sum 
ar_data$daily_preparation_of_GC_to_use_original <- ar_data$daily_preparation_of_GC_to_use
ar_data$absolute_total_daily_hydrocortisone_at_visit_original <- ar_data$absolute_total_daily_hydrocortisone_at_visit
ar_data$absolute_total_daily_prednisolone_at_visit_original <- ar_data$absolute_total_daily_prednisolone_at_visit
ar_data$absolute_total_daily_prednisone_at_visit_original <- ar_data$absolute_total_daily_prednisone_at_visit
ar_data$absolute_total_daily_dexamethasone_at_visit_original <- ar_data$absolute_total_daily_dexamethasone_at_visit
ar_data$absolute_total_daily_other_GC_at_visit_original <- ar_data$absolute_total_daily_other_GC_at_visit
ar_data$total_daily_hydrocortisone_equivalent_at_visit_original <- ar_data$total_daily_hydrocortisone_equivalent_at_visit
ar_data$fludrocortisone_dose_original <- ar_data$fludrocortisone_dose
ar_data$total_daily_fludro_dose_original <- ar_data$total_daily_fludro_dose
descr(ar_data$total_daily_fludro_dose)
```


```{r, correction of Glucocorticoids...Current.Medication if we have dose data}
ar_data$Glucocorticoids...Current.Medication <-
  ifelse(!is.na(ar_data$daily_preparation_of_GC_to_use) &
           ar_data$daily_preparation_of_GC_to_use!="none",
         "Yes",
         ar_data$Glucocorticoids...Current.Medication)
```


```{r, calculate number after joining everything for comparison later}
number_of_rows_before_join <- 
  nrow(ar_data)
```

Now that we have all of the visits included in all four frames, we can calculate our earliest and oldest visits and join them into the ar_data frame

```{r, attach youngest visit date and oldest visit date to each row of a patient}
youngest_visits <- 
  ar_data %>% 
  group_by(id) %>% 
  slice_min(visit_date, 
            with_ties = F)

print("total number of participants in ar_data youngest visit frame")

nrow(youngest_visits)

youngest_visits_to_join <- 
  youngest_visits[,c("id", 
                     "visit_date")]

#freq(youngest_visits_to_join$id)
#no problem with ids in that frame

names(
  youngest_visits_to_join)[
    names(youngest_visits_to_join)=="visit_date"] <- 
  "earliest_visit_date"

oldest_visits <- 
  ar_data %>% 
  group_by(id) %>% 
  slice_max(visit_date, with_ties = F)

#freq(oldest_visits_to_join$id)
#no problem with ids in that frame

oldest_visits_to_join <- 
  oldest_visits[,c("id", 
                   "visit_date")]

names(oldest_visits_to_join)[names(oldest_visits_to_join)=="visit_date"] <- 
  "oldest_visit_date"

print("total number of participants in ar_data oldest visit frame")

nrow(oldest_visits)

total_number_of_visits_to_join <- 
  oldest_visits[,c("id", "visit_date")]

names(oldest_visits_to_join)[names(oldest_visits_to_join)=="visit_date"] <- 
  "oldest_visit_date"

print("total number of participants in ar_data oldest visit frame")

nrow(oldest_visits)

```

```{r, create oldest_visits_before_20}
oldest_visits_before_20 <- 
  subset(ar_data, Decimal.age.at.visit..calculated.by.formula..YEARFRAC.DOB.DOV..<20) %>%
  group_by(id) %>% 
  slice_max(visit_date, 
            with_ties = F)

oldest_visits_before_20_to_join <- 
  oldest_visits_before_20[,c("id", 
                             "visit_date")]


names(oldest_visits_before_20_to_join)[names(oldest_visits_before_20_to_join)=="visit_date"] <-
  "oldest_visit_date_before_20"
```

```{r, add oldest and youngest visits back to ar_data frame}
ar_data_with_youngest_oldest <- 
  dplyr::left_join(ar_data, 
                   youngest_visits_to_join, 
                   by="id")

ar_data_with_youngest_oldest <- 
  dplyr::left_join(ar_data_with_youngest_oldest, 
                   oldest_visits_to_join, 
                   by="id")

ar_data_with_youngest_oldest <- 
  dplyr::left_join(ar_data_with_youngest_oldest, 
                   oldest_visits_before_20_to_join, 
                   by="id")

ar_data <- ar_data_with_youngest_oldest

```

Now we calculate the total_years_of_data_for_id

```{r, calculate years of data in the registry for each patient}
ar_data$total_years_of_data_for_id <- 
  as.numeric(ar_data$oldest_visit_date - 
               ar_data$earliest_visit_date) / 60 / 60 / 24 / 365.25

ar_data$total_years_of_data_before_20_for_id <- 
  as.numeric(ar_data$oldest_visit_date_before_20 - 
               ar_data$earliest_visit_date) / 60 / 60 / 24 / 365.25

print("description of years of follow up in patients under 20 years of age")

descr(ar_data$total_years_of_data_before_20_for_id)
```

just take out one visit per patient in order to describe the number of years follow up

```{r, describe number of years follow up into text file}
dir.create("ICAH BP text file outputs")

sink("./ICAH BP text file outputs/descriptions_of_number_of_years_of_follow_up.txt")

recent_visits <- 
  ar_data %>% 
  group_by(id) %>% 
  slice_max(Decimal.age.at.visit..calculated.by.formula..YEARFRAC.DOB.DOV.., n=1, with_ties=F)

recent_visits_before_20 <- 
  subset(recent_visits, 
         Decimal.age.at.visit..calculated.by.formula..YEARFRAC.DOB.DOV..<20)

descr(recent_visits_before_20$total_years_of_data_before_20_for_id)
freq_centres <- 
  subset(rownames_to_column(as.data.frame(freq(recent_visits_before_20$Centre.Name...Centre))), 
         rowname!= "Total" & rowname!="<NA>")

print("Description of number of patients per centre under 20 years old")

descr(freq_centres$Freq)

recent_visits_before_20_male <- 
  subset(recent_visits_before_20, 
         sex_1_for_M_2_for_F==1)

freq_centres_male <- 
  subset(rownames_to_column(as.data.frame(freq(recent_visits_before_20_male$Centre.Name...Centre))), 
         rowname!= "Total" & 
           rowname!="<NA>")

print("Description of number of male patients per centre under 20 years old")

descr(freq_centres_male$Freq)

recent_visits_before_20_female <- 
  subset(recent_visits_before_20, 
         sex_1_for_M_2_for_F==2)

freq_centres_female <- 
  subset(rownames_to_column(as.data.frame(freq(recent_visits_before_20_female$Centre.Name...Centre))),
         rowname!= "Total" & 
           rowname!="<NA>")

print("Description of number of female patients per centre under 20 years old")

descr(freq_centres_female$Freq)

sink()
```

```{r, check joining earliest and recent visit dates hasnt duplicated rows}
print("number of rows in ar_data frame before earliest and oldest visit calculations and join:")
number_of_rows_before_join

print("number of rows in ar_data frame after earliest and oldest visit calculations and join:")
nrow(ar_data)

```

```{r, rationalise columns in data, this will stop the file becoming quite so data intensive}
#we now know we have all the data in one frame, but to make it manageable, we now need to rationalise our columns
sink("colnames_before_removal.txt")
colnames(ar_data)
sink()

#we have created other variables for these

ar_data$Date...CAH.Longitudinal.Data <- NULL 

ar_data$Weight..kg....CAH.Longitudinal.Data <- NULL 

ar_data$Height..cm....CAH.Longitudinal.Data <- NULL 

ar_data$Register.ID...Record <- NULL 

freq(ar_data$Date.of.birth...Birth)
ar_data$Date.of.birth...Birth <- NULL 

#the following fields are poorly completed

freq(ar_data$Waist.circumference..cm....CAH.Longitudinal.Data)
ar_data$Waist.circumference..cm....CAH.Longitudinal.Data <- NULL 

freq(ar_data$Hip.circumference..cm....CAH.Longitudinal.Data)
ar_data$Hip.circumference..cm....CAH.Longitudinal.Data <- NULL 

freq(ar_data$Number.of.pregnancies.in.the.past...Puberty.Female)
ar_data$Number.of.pregnancies.in.the.past...Puberty.Female <- NULL 

freq(ar_data$Number.of.live.births...Puberty.Female)
ar_data$Number.of.live.births...Puberty.Female <- NULL 

freq(ar_data$Birth.head.circumference..cm....Birth)
ar_data$Birth.head.circumference..cm....Birth <- NULL 

freq(ar_data$Data.can.be.shared.for.research.purposes...Consent)
ar_data$Data.can.be.shared.for.research.purposes...Consent <- NULL 

freq(ar_data$Current.gender...Details.of.Condition)
ar_data$Current.gender...Details.of.Condition <- NULL 

freq(ar_data$Karyotype...Details.of.Condition)
ar_data$Karyotype...Details.of.Condition <- NULL 

freq(ar_data$Disorder.type...Details.of.Condition)
ar_data$Disorder.type...Details.of.Condition <- NULL 

freq(ar_data$Actual.diagnosis...Details.of.Condition)
ar_data$Actual.diagnosis...Details.of.Condition <- NULL 

freq(ar_data$Specify.the.actual.diagnosis...Details.of.Condition)
ar_data$Specify.the.actual.diagnosis...Details.of.Condition <- NULL 

freq(ar_data$Date.of.condition.onset...Details.of.Condition)
ar_data$Date.of.condition.onset...Details.of.Condition <- NULL 

freq(ar_data$Diagnostic.biochemistry...Details.of.Condition)
ar_data$Diagnostic.biochemistry...Details.of.Condition <- NULL 

unique(ar_data$Diagnostic.biochemistry.additional.details...Details.of.Condition)
ar_data$Diagnostic.biochemistry.additional.details...Details.of.Condition <- NULL 

freq(ar_data$Diagnostic.genetics...Details.of.Condition)
ar_data$Diagnostic.genetics...Details.of.Condition <- NULL 

unique(ar_data$Diagnostic.genetics.additional.details...Details.of.Condition)
ar_data$Diagnostic.genetics.additional.details...Details.of.Condition <- NULL

freq(ar_data$Participation.in.Other.Registries...Details.of.Condition)
ar_data$Participation.in.Other.Registries...Details.of.Condition <- NULL 

freq(ar_data$Details.of.Registry.and.ID...Details.of.Condition)
ar_data$Details.of.Registry.and.ID...Details.of.Condition <- NULL 

freq(ar_data$History.of.similar.condition...Family)
ar_data$History.of.similar.condition...Family <- NULL 

freq(ar_data$Date.of.death...Death)
ar_data$Date.of.death...Death <- NULL 

freq(ar_data$Section...Death)
ar_data$Section...Death <- NULL 

freq(ar_data$Cause.of.death...Death)
ar_data$Cause.of.death...Death <- NULL 

freq(ar_data$Record...CAH.First.Presentation)
ar_data$Record...CAH.First.Presentation <- NULL 

freq(ar_data$Prenatal.diagnosis...CAH.First.Presentation)
ar_data$Prenatal.diagnosis...CAH.First.Presentation <- NULL 

unique(ar_data$Additional.details...CAH.First.Presentation)
ar_data$Additional.details...CAH.First.Presentation <- NULL 

freq(ar_data$Salt.wasting.crisis.at.presentation...CAH.First.Presentation)
ar_data$Salt.wasting.crisis.at.presentation...CAH.First.Presentation <- NULL 

freq(ar_data$Adrenal.crisis.at.first.presentation...CAH.First.Presentation)
ar_data$Adrenal.crisis.at.first.presentation...CAH.First.Presentation <- NULL 



#the following fields are not directly of use
freq(ar_data$Cushingoid...CAH.Longitudinal.Data)
ar_data$Cushingoid...CAH.Longitudinal.Data <- NULL 

freq(ar_data$Virilisation...CAH.Longitudinal.Data)
ar_data$Virilisation...CAH.Longitudinal.Data <- NULL 

freq(ar_data$Anaemia...Comorbid.Conditions.and.Surgery)
ar_data$Anaemia...Comorbid.Conditions.and.Surgery <- NULL 

freq(ar_data$Anaemia.note...Comorbid.Conditions.and.Surgery)
ar_data$Anaemia.note...Comorbid.Conditions.and.Surgery <- NULL 

freq(ar_data$Depression...Comorbid.Conditions.and.Surgery)
ar_data$Depression...Comorbid.Conditions.and.Surgery <- NULL 

unique(ar_data$Depression.note...Comorbid.Conditions.and.Surgery)
ar_data$Depression.note...Comorbid.Conditions.and.Surgery <- NULL 

freq(ar_data$Anxiety...Comorbid.Conditions.and.Surgery)
ar_data$Anxiety...Comorbid.Conditions.and.Surgery <- NULL 

freq(ar_data$Anxiety.note...Comorbid.Conditions.and.Surgery)
ar_data$Anxiety.note...Comorbid.Conditions.and.Surgery <- NULL 

freq(ar_data$Psychosis...Comorbid.Conditions.and.Surgery)
ar_data$Psychosis...Comorbid.Conditions.and.Surgery <- NULL 

freq(ar_data$Psychosis.note...Comorbid.Conditions.and.Surgery)
ar_data$Psychosis.note...Comorbid.Conditions.and.Surgery <- NULL 

freq(ar_data$Other.mental.health.problems...Comorbid.Conditions.and.Surgery)
ar_data$Other.mental.health.problems...Comorbid.Conditions.and.Surgery <- NULL 

freq(ar_data$Other.mental.health.problems.note...Comorbid.Conditions.and.Surgery)
ar_data$Other.mental.health.problems.note...Comorbid.Conditions.and.Surgery <- NULL 

freq(ar_data$Joint.hypermobility...Comorbid.Conditions.and.Surgery)
ar_data$Joint.hypermobility...Comorbid.Conditions.and.Surgery <- NULL 

freq(ar_data$Joint.hypermobility.note...Comorbid.Conditions.and.Surgery)
ar_data$Joint.hypermobility.note...Comorbid.Conditions.and.Surgery <- NULL 

freq(ar_data$Other...Comorbid.Conditions.and.Surgery)
ar_data$Other...Comorbid.Conditions.and.Surgery <- NULL 

unique(ar_data$Other.note...Comorbid.Conditions.and.Surgery)
ar_data$Other.note...Comorbid.Conditions.and.Surgery <- NULL 

freq(ar_data$Antidiabetic...Current.Medication)
ar_data$Antidiabetic...Current.Medication <- NULL 

freq(ar_data$Antidiabetic.note...Current.Medication)
ar_data$Antidiabetic.note...Current.Medication <- NULL 

freq(ar_data$Antidepressants...Current.Medication)
ar_data$Antidepressants...Current.Medication <- NULL 

unique(ar_data$Antidepressants.note...Current.Medication)
ar_data$Antidepressants.note...Current.Medication <- NULL 

freq(ar_data$Other.drugs...Current.Medication)
ar_data$Other.drugs...Current.Medication <- NULL 

unique(ar_data$Other.drugs.note...Current.Medication)
ar_data$Other.drugs.note...Current.Medication <- NULL 

freq(ar_data$Patient.follow.up.status...Record)
ar_data$Patient.follow.up.status...Record <- NULL 

freq(ar_data$First.contact.with.centre...Record)
ar_data$First.contact.with.centre...Record <- NULL 

freq(ar_data$Country.at.birth...Birth)
ar_data$Country.at.birth...Birth <- NULL 

freq(ar_data$Mid.Parental.Height)
ar_data$Mid.Parental.Height <- NULL 

sink("colnames_after_removal.txt")
colnames(ar_data)
sink()

```

We can now take that forward and load previous decimal ages in the next file to model ages from previous decimal ages for those with spurious dates of birth

```{r, take this file as opportunity to rationalised files being saved}
rm(ar_participants)

rm(ar_participants_base_data)

rm(ar_participants_longitudinal_data)

rm(ar_labs_wide)

rm(ar_meds_wide)

rm(ar_fludro_wide)

rm(ar_participants_longitudinal_data)

```


```{r, end of file so save all the listed dataframes into the parent directory}
#save a csv file in this case as we have finally joined, for review
write.csv(ar_data, "ar_data_after_file_10.csv", row.names=F)

rm(prednisolone_to_hydrocortisone_conversion)
rm(dexamethasone_to_hydrocortisone_conversion)
rm(cortisone_acetate_to_hydrocortisone_conversion)
rm(methylprednisolone_to_hydrocortisone_conversion)

save_ar_files_function(
  parent_directory=location_of_data_files,
  parent_file="file_10")

Sys.time()
nrow(ar_data)


```
